Capturing the geometric structure of our experiences and how we remember them

### 2018-07-24 main.tex
checking in work

\subsubsection{Brain regions that mirror the correlational structure of memory}

>>>>

\subsubsection{Brain regions that mirror the correlational structure of naturalistic memories}.
While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events. For example, the event by event similarity structure (e.g. the off-diagonal values of the recall correlation matrices) differed by individual (Supp. Fig.~\ref{fig:corrmats}). In the final analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.

The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}. This makes it challenging to use the recall model directly to examine neural activity patterns during video viewing.  To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW ref).  We used the resulting path warp each voxel's timeseries as well as the recall model timeseries.  Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint correlation matrix over searchlight voxels. We vectorized the recall correlation and searchlight correlation.
